On the minimum leaf conductance

### 2017-08-13 manuscript.Rmd
Some references added; bug fix in load
more writing; one ref added

@@

\
Here we review the various options to estimate g~0~ for use in models of plant water use and carbon uptake. We place an emphasis on sources of variation in g~min~, and the role that g~min~ can play in models of water use. Before we discuss the various definitions and measurements of minimum conductance, we first review the modelling literature on its use of g~0~ in Eq. 1 (and related approaches), and demonstrate why g~0~ needs to be included in models.

@@

\
Measurements of conductance of isolated, non-stomatal cuticles (g~cut~) were taken from the compilation by @kerstiens1996. Data on minimum conductance (g~min~) from weight loss of detached leaves was compiled from XXX papers, see Appendix. A compilation of night-time (and 'dark') conductance (g~dark~) values was taken from @lombardozzi2017. We also estimated g~0~ for each study included in a large database of leaf gas exchange data [@lin2015], by fitting Eq. 1 using the stomatal conductance model of @medlyn2011. These estimates were combined with the compilation of g~0~ values from @miner2017, who reported on xxx values from a literature compilation (each of those values was estimated with linear regression of the Ball-Berry model). Finally, we also estimated minimum values of g~s~ attained from the Lin et al. database, by taking those data where A~n~ < 2 $mu$ mol m^-2^ s^-1^, and calculating the minimum g~s~ for each of the XXX studies included in that dataset. This estimate was added as it represents an actual minimum values measured, rather than a fitted/extrapolated g~0~ term.

\
It is customary for g~cut~ and g~min~ to be expressed per unit total leaf surface area, however, since we aim a comparison with g~0~ and g~dark~, all values were converted to per unit projected surface area. Units were converted to molar fluxes assuming 41 mol m^-3^ (cf. @kerstiens1996). For the combined dataset, we looked up plant growth form and phylogenetic group (angiosperm or gymnosperm) from the TRY categorical traits database [@kattge2011], and taxonomic family and order with the taxize R package [@chamberlain2013].

g~s,low A~ much lower than fitted g~0~ or g~dark~ (see also @dekauwe2015, their Fig. A2).

g~dark~ much higher than g~min~, also confirmed by experiments. In soybean, @waldencoleman2013 showed much higher g~dark~  compared to g~min~.

@korner1994 table of minimum conductance. Also points out (without reference) that g0 in droughted leaves is certainly lower than g0 in dark or very high CO2 leaves.

@@

@@

#  Cuticular conductance

The conductance of stomata-free leaf cuticles represents the absolute minimum conductance that leaves can attain. It is clear from our literature review, g~cut~ is very much lower than other definitions of minimum conductance - it is on average twice as low as g~min~. We admit some caution in this conclusion, because g~cut~ is probably too low in the way it is measured (as a permeance), due to low water content of the cuticle in those conditions [@kerstiens1996]. We briefly review a few important aspects of cuticular conductance, and to what extent we expect it to vary with species and environments. We refer to previous in-depth reviews for a more detailed treatment of other aspects of plant cuticles, such as chemical composition and morphology, and modes of water transport across the cuticle [@kerstiens1996; @kerstiens2006; @schreiber1996; @schreiber2001; @schuster2016b].

Although we use the term cuticular conductance freely, this transport pathway does not represent a true conductance since water does not diffuse as a gas through the cuticle. Instead, it dissolves into the medium of the cuticle, diffuses through the solid matrix, and is desorped at the outer edge of the cuticle. The main barrier to diffusion is actually a very thin layer at the leaf surface. Because most of the resistance is located in such a thin layer, g~cut~ does not depend on the thickness of the cuticle  [@riederer2001; @anfodillo2002]. One may ask why there is so much variation in cuticle thickness between plant species, if it does not affect g~cut~. The answer may lie in mechanical strength rather than water relations, as @onoda2012 reported that thicker cuticles are more resistant to tearing (the force to tear and tensile strength both approx proportional to cuticle thickness).

Despite considerable work on the topic, no clear relationship between chemical composition or structure of the cuticle and its conductance has emerged. Recently, @schuster2016a presented a comprehensive study of cuticle chemical composition, but this variation could not explain variation in cuticular conductance (gcutisol). Similarly, @hauke1998 found no relationship between the gradual decrease in g~cut~ in *Hedera helix* during leaf maturation and cuticle wax amount, mean chain lengths, or cuticle weight.

Water travels more freely across the cuticle than CO2 [@boyer1997; @boyer2015]
This observation was used by @manzoni2011 to recalculate leaf water-use efficiency for droughted plants, but we caution against this because g~cut~ is only one component of g~min~, and CO~2~ will travel through leaky and incompletely closed stomata.

>>>>

@bi2017 lower residual transpiration rate in drought-acclimated wheat, in 3 out of 4 genotypes. Drought caused a change in cuticular wax production and chemical composition, but in a highly genotype-specific way.

@@

\
Here we review a) the role and current use of g~0~ in models, b) various definitions of minimum conductance and comparison of literature values, c) sources of variation in minimum conductance.

@@

@@

Because estimation of g~0~ is problematic, this begs the question whether suitable estimates of minimum conductance can be arrived at from independent measurements. Measurements of minimum conductance, after stomatal closure is either induced or assumed, can be broadly divided into the following categories. The absolute minimum conductance attained by leaves is that through the cuticle only. Measurements of cuticular conductance (g~cut~) are typically made on isolated cuticles [@riederer2001], or on the side of the leaf that lacks stomata ('adaxial' side). Previous work has thoroughly summarized mechanisms and sources of variation in g~cut~, which will not be repeated in this review. We briefly summarize some important points in SectionXXX.

\
A more common measurement is to detach leaves, and measure leaf weight over time as the leaf dries out. After some time, a constant minimum transpiration rate is attained (sometimes described as the 'residual transpiration rate'), from which minimum conductance (g~min~) can be inferred using measured vapour pressure deficit. Because this method most closely resembles conditions that plants may experience during a dry-down or periods of extreme stress, it is perhaps the most promising as an independent measurement of minimum conductance. Because night-time conductance (g~dark~) is frequently used as an independent measurement of g~0~, we compare literature values of g~dark~ with g~min~ and g~cut~, as well as the compilation of fitted values of g~0~ (already shown in Figs X and Y). A final minimum conductance was estimated from the @lin2015 database by extracting actual minimum daytime alues measured, when photosynthetic rates were low.

\
Measurements of conductance of isolated, non-stomatal cuticles (g~cut,isol~), and of conductance of detached leaves with the stomatal side sealed (g~cut,seal~) were taken from the compilation by @kerstiens1996. Technically speaking this is not a conductance, but a 'permeance' because water does not *diffuse* across cuticle [@kerstiens1996]. Data on minimum conductance (g~min~) from weight loss of detached leaves was compiled from XXX papers, see Appendix for a list of papers. For the compilation, we returned to all original papers mentioned in the review by @kerstiens1996, and added many newer sources. A compilation of night-time conductance (g~dark~) values was taken from @lombardozzi2017, who compiled cuvette (and sometimes sap flow-based) measurements of ca. 150 species during night-time. Actual minimum daytime values were estimated from the Lin et al. database, by taking those data where A~n~ < 2 $mu$ mol m^-2^ s^-1^, and calculating the minimum g~s~ for each of the XXX studies included in that dataset. This estimate was added as a reference as it represents an actual minimum values measured, rather than a fitted/extrapolated g~0~ term.

\
All conductance values were converted to per unit projected surface area. Units were converted to molar fluxes assuming 41 mol m^-3^ (cf. @kerstiens1996). For the combined dataset, we looked up plant growth form and phylogenetic group (angiosperm or gymnosperm) from the TRY categorical traits database [@kattge2011] (manually filling in numerous gaps), and taxonomic family and order with the taxize R package [@chamberlain2013].

The broad comparison between the various estimates of conductance (FigXX) highlights a number of key features, discussed below.

### Low conductance of isolated cuticles

Literature values of g~cut~ were much lower than any other estimate of conductance, even compared to measurements based on MLD with stomatal side sealed (g~mld,seal~). The conductance of stomata-free leaf cuticles represents the absolute minimum conductance that leaves can attain. This result should be viewed with caution as @kerstiens1996 argued that measurements of g~cut~ maybe too low due to low water content of the cuticle after detachment from the leaf, and storage in often dry-air conditions [@kerstiens1996]. A review of cuticular transport mechanisms, biochemical composition, and formation of cuticular waxes is well outside the scope of this review, and refer to previous work [@kerstiens1996; @kerstiens2006; @shepherd2006; @schreiber1996; @schreiber2001; @schuster2016b]. However, a few key points should be reiterated.

Although we use the term cuticular conductance freely, this transport pathway does not represent a true conductance since water does not diffuse as a gas through the cuticle. Instead, it dissolves into the medium of the cuticle, diffuses through the solid matrix, and is desorped at the outer edge of the cuticle. The main barrier to diffusion is actually a very thin layer at the leaf surface. Because most of the resistance is located in such a thin layer, g~cut~ does not depend on the thickness of the cuticle  [@riederer2001; @anfodillo2002; @schuster2016b]. One may ask why there is so much variation in cuticle thickness between plant species, if it does not affect g~cut~. Perhaps the answer lies in mechanical strength rather than water relations, as @onoda2012 reported that thicker cuticles are more resistant to tearing (the force to tear and tensile strength both approx proportional to cuticle thickness).

Despite considerable work on the topic, no clear relationship between chemical composition or structure of the cuticle and its conductance has emerged. Recently, @schuster2016a presented a comprehensive study of cuticle chemical composition, but this variation could not explain variation in g~cut~. Similarly, @hauke1998 found no relationship between the gradual decrease in g~cut~ in *Hedera helix* during leaf maturation and cuticle wax amount, mean chain lengths, or cuticle weight.

Water travels more freely across the cuticle than CO2 [@boyer1997; @boyer2015]. This observation was used by @manzoni2011 to recalculate leaf water-use efficiency for droughted plants, but we caution against this because g~cut~ is only one component of g~min~, and CO~2~ will travel through leaky and incompletely closed stomata.

2. g~s,low A~ much lower than fitted g~0~ or g~dark~. In other words, actual daytime conductance is much lower than the presumed minimum estimated from fitted g~0~. A similar result was already presented by @dekauwe2015 (their  Fig. A2).
3. g~dark~ on average eight-fold higher than g~min~. Not many studies measure both g~dark~ and g~min. In soybean, @waldencoleman2013 showed much higher g~dark~  compared to g~min~. @koerner1994 also states that g~s~ in droughted leaves is certainly lower than g~s~ in the dark.

@@
